Modeling browser-based distributed evolutionary computation systems

### 2015-02-08 modeling-volunteer-computing-gecco.tex
Adding graphs with results

In fact, the program includes more logic to serve the static pages
that contain the talk in which it is included and the JavaScript/CSS
code also, but it all amounts to a small amount of code. This code can
be deployed, in principle, in any server running node.js, but for the
purposes of this experiment Heroku, a Platform as a Service with a
free tier, has been chosen. It could be also be deployed, with small
or no modification, to OpenShift or other similar PaaS. Far from being
a freeriding way, using free or very low cost servers can be a
sustainable way of performing massive distributed evolutionary
computation experiments \cite{Merelo2014}

@@

As indicated in the introduction, every part of the experiment and
data gathered have been released as free software in a GitHub
repository (address hidden for double blind review).

@@

>>>>

In fact, the program includes more logic to serve the static pages
that contain the talk in which it is included and the JavaScript/CSS
code also, but it all amounts to a small amount of code. This code can
be deployed, in principle, in any server running node.js, but for the
purposes of this experiment Heroku, a Platform as a Service with a
free tier, has been chosen. It could be also be deployed, with small
or no modification, to OpenShift or other similar PaaS. Far from being
a freeriding way, using free or very low cost servers can be a
sustainable way of performing massive distributed evolutionary
computation experiments \cite{Merelo2014,jj:idc:lowcost}.

@@

As indicated in the introduction, every part of the experiment and
data gathered have been released as free software in a GitHub
repository (address hidden for double blind review). These results
will be analyzed in the next section.

@@

The litmus test that all experiments should pass, that is, that they
work and found the solution, passed. In fact, the first version of the
algorithm (until January 2015) used too much memory on the browser,
which crashed after a while running. A total of 7 experiments were
done with this version. After January, a new version of the
evolutionary algorithm with non-cached fitness was used which did not
crash the browser and was thus allowed to run as much time as
needed. That was the version used in a lightning talk at the beginning
of February. A total of 10 experiments were made with this second
version. In the first version, finding the solution took a few
minutes. The second needed around 20 minutes. In the logs used, it was
not checked that the algorithm had found the solution, but in most
cases it had. More systematic experimentation would have to wait until
the next version, since in this first one we were looking for some
kind of systematicity in the behavior of users and the experimental
apparatus is the minimum possible to have it running.
%
\begin{figure*}[htb]
        \centering
        \subfigure[First experiment]{
                \includegraphics[width=0.45\linewidth]{data/diffs-ips-1.png}
                \label{fig:e1_p}
        }
        \subfigure[Second experiment]{
                \includegraphics[width=0.45\linewidth]{data/diffs-ips-2.png}
                \label{fig:e2_p}
        }
        \caption{Histogram of number of different IPs in an experiment}\label{fig:histo:ips}
\end{figure*}

The fact that it run correctly during a massive lightning talk means that this setup is a
valid, no-cost, platform for massive evolutionary algorithms. There
were several ways of introducing it: during a talk, telling the
audience to visit the web that was posted in the first slide, and
after the talk, inserting the URL in a tweet with a brief explanation
and several tweets more indicating what it was about and what it
did. If any question arose, it was answered as fast as possible.
